### 2018-05-07 Main.Rmd
Fixed bug in argument name to helper function.

```{r}
#Import data form wordbank in a format that will be useful for us (especially when we will do development in time).

@@

#Extract the list of all uni_lemmas (like Hills, we will start with the analysis of all words first)
lemma_list<- wb_data %>%
  trim_all_unilemma() %>% #We do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication
  filter(age==first_age) %>% #Since the fisrt month in our format is the month when all words are stil present 
  select(item, uni_lemma)

>>>>

```{r}
#Import data from wordbank in a format that will be useful for us (especially when we will do development in time).

@@

#Extract the list of all uni_lemmas (like Hills, we will start with the analysis of all words first)
lemma_list<- wb_data %>%
  trim_all_unilemma() %>% #We do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication
  filter(age==first_age) %>% #Since the first month in our format is the month when all words are stil present 
  select(item, uni_lemma)
